Mass surveillance in cyberspace and the lost art of keeping a secret\thanks{The ideas discussed here first appeared as a DCSS project conference talk and were subsequently fleshed out in paper due to serendipitous encounters fostered by twitter.}

### 2015-07-08 edemocracy.tex
Final commit. Really.

\title{Mass surveillance in cyberspace and the lost art of keeping a secret\thanks{The ideas presented in this paper first appeared as a talk at the 2015 Conference on Digital Citizenship and Surveillance Society in Cardiff in June 2015 and subsequently refined and developed into this paper via serendipitous encounters that were enabled by the social medium of Twitter. The work has been sponsored in part by the European Commission through project NIFTy (ISEC 2012 Action Grants HOME/2012/ISEC/INT/4000003892).}}
\subtitle{Policy lessons for Government after the Snowden leaks}

@@

\bibitem{Ball}
Ball, C.:
Organization, surveillance and the body: Towards a politics of resistance. In: Lyon, David ed. Theorising Surveillance: The Panopticon and beyond. Collumpton, UK: Willan Publishing.

\bibitem{Greenwald}
Greenwald, G.:
No Place to Hide: Edward Snowden, the NSA and the Surveillance State, Hamish Hamilton, 2014

@@

\bibitem{gosling:2009}
Gosling, S.:
\newblock {Snoop: What Your Stuff Says About You}.
\newblock {Profile Books} (2009)

\bibitem{oatley+crick:2014}
Oatley, G. and Crick, T.:
\newblock {Changing Faces: Identifying Complex Behavioural Profiles}.
\newblock In {\em {Human Aspects of Information Security, Privacy and Trust}},
  volume 8533 of {\em {Lecture Notes in Computer Science}}, pages 282--293.
  Springer, 2014.

@@

\bibitem{keepingukcybersafe:2014}
{Cabinet Office}.
\newblock {Keeping the UK safe in cyber space}.
\newblock {UK Government}, December 2014.

@@

\bibitem{ECDH}
Hales, T.:
The NSA Back Door to NIST, Notices of the AMS, Vol. 61, No 2, 191--192, February 2014

@@

\bibitem{Ditton}
Ditton, J.:
Crime and the City, British Journal of Criminology, 40(4), 692-709, 2000

@@

\bibitem{Lobban}
Lobban, I.:
Sir Iain Lobban's valedictory speech - as delivered, GCHQ website, 2014

@@

\bibitem{Anastasopoulou}
Anastasopoulou, K., Tryfonas, T. \& Kokolakis, S.:
Strategic stakeholder interaction analysis of cloud-based mobile applications use of privacy-sensitive end users, Lecture Notes in Computer Science, Springer, Vol. 8030, 209-216, 2013.

>>>>

\title{Mass surveillance in cyberspace and the lost art of keeping a secret\thanks{This work has been supported in part by the European Commission through project NIFTy (ISEC 2012 Action Grants HOME/2012/ISEC/INT/4000003892). The ideas discussed appeared first as a talk at the Digital Citizenship and Surveillance Society project conference in Cardiff in June 2015. They were subsequently refined into this paper partly via serendipitous encounters enabled by the social medium of Twitter.}}
\subtitle{Policy lessons for Government after the Snowden leaks}

@@

\bibitem{Ball}
Ball, C.:
Organization, surveillance and the body: Towards a politics of resistance. In: Lyon, David ed. Theorising Surveillance: The Panopticon and beyond. Collumpton, UK: Willan Publishing, 2006.

\bibitem{Greenwald}
Greenwald, G.:
No Place to Hide: Edward Snowden, the NSA and the Surveillance State, Hamish Hamilton, 2014.

@@

\bibitem{gosling:2009}
Gosling, S.:
\newblock {Snoop: What Your Stuff Says About You}.
\newblock {Profile Books} 2009

\bibitem{oatley+crick:2014}
Oatley, G. and Crick, T.:
\newblock {Changing Faces: Identifying Complex Behavioural Profiles}.
\newblock In {\em {Human Aspects of Information Security, Privacy and Trust}}, Lecture Notes in Computer Science Vol. 8533, pp. 282--293.
  Springer, 2014.

@@

\bibitem{keepingukcybersafe:2014}
{Cabinet Office}.
\newblock {Keeping the UK safe in cyber space}.
\newblock {UK Government}, Dec. 2014

@@

\bibitem{ECDH}
Hales, T.:
The NSA Back Door to NIST, Notices of the AMS, 61(2), 191--192, February 2014

@@

\bibitem{Ditton}
Ditton, J.:
Crime and the City, British Jnl of Criminology, 40(4), 692-709, 2000

@@

\bibitem{Lobban}
Lobban, I.:
Sir Iain Lobban's valedictory speech as delivered, GCHQ website, 2014

@@

\bibitem{Anastasopoulou}
Anastasopoulou, K., Tryfonas, T. \& Kokolakis, S.:
Strategic stakeholder interaction analysis of cloud-based mobile applications use of privacy-sensitive end users, In {\em {Human Aspects of Information Security, Privacy and Trust}}, Lecture Notes in Computer Science Vol. 8030, Springer, 209-216, 2013.
